### 2020-01-22 experiments.tex
p

\begin{enumerate}
\item {\bf Boolean constant misuse:}  This detector flags code like {\tt if (true}} or {\tt g(b || true)} (where {\tt g} is a function that takes a Boolean input).  Constant-valued conditionals tend to indicate debugging efforts that have persisted into production code, or other faults; there are almost no circumstances where a conditional should not vary with state or input.  This detector is actually split into two detectors, one for this serious issue, and an informational/stylistic detector that notes that code such as {\tt if (x == true)}, while semantically harmless, is difficult to read.  This problem was easily identified from cases such as this mutant, killed by SmartCheck but not Slither:

\begin{code}
0x598ab825d607ace3b00d8714c0a141c7ae2e6822_Vault.mutant.275.sol: 424contracts//0x598ab825d607ace3b00d8714c0a141c7ae2e6822_Vault.sol:249
        if (!p.recipient.send(p.amount)) \{  // Make the payment
 ==>          if (true) \{  // Make the payment
        if (true) {  // Make the payment
\end{code}

@@

\begin{code}
0x968815CD73647C3af02a740a2438D6f8219e7534_TTPresale.mutant.311.sol: 424contracts//0x968815CD73647C3af02a740a2438D6f8219e7534_TTPresale.sol:175
        require(nextDiscountTTMTokenId6 >= 361 && nextDiscountTTMTokenId6 <= 391);
 ==>  ...361...==>...0...
        require(nextDiscountTTMTokenId6 >= 0 && nextDiscountTTMTokenId6 <= 391);
\end{code}

@@

\begin{code}
0x534ccee849a688581d1b0c65e7ff317ed10c5ed3_NametagToken.mutant.480.sol: 424contracts//0x534ccee849a688581d1b0c65e7ff317ed10c5ed3_NametagToken.sol:650
        byte char = byte(bytes32(uint(x) * 2 ** (8 * j)));
 ==>  ...*...==>.../...
        byte char = byte(bytes32(uint(x) * 2 ** (8 / j)));
\end{code}

>>>>

\begin{enumerate}
\item {\bf Boolean constant misuse:}  This detector flags code like {\tt if (true)} or {\tt g(b || true)} (where {\tt g} is a function that takes a Boolean input).  Constant-valued conditionals tend to indicate debugging efforts that have persisted into production code, or other faults; there are almost no circumstances where a conditional should not vary with state or input.  This detector is actually split into two detectors, one for this serious issue, and an informational/stylistic detector that notes that code such as {\tt if (x == true)}, while semantically harmless, is difficult to read.  This problem was easily identified from cases such as this mutant, killed by SmartCheck but not Slither:

\begin{code}
0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.mutant.275.sol: 424contracts//0x598ab825d607ace3b00d8714c0a141c7ae2e6822\_Vault.sol:249
        if (!p.recipient.send(p.amount)) \{  // Make the payment
 ==>          if (true) \{  // Make the payment
        if (true) \{  // Make the payment
\end{code}

@@

\begin{code}
0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.mutant.311.sol: 424contracts//0x968815CD73647C3af02a740a2438D6f8219e7534\_TTPresale.sol:175
        require(nextDiscountTTMTokenId6 >= 361 \&\& nextDiscountTTMTokenId6 <= 391);
 ==>  ...361...==>...0...
        require(nextDiscountTTMTokenId6 >= 0 \&\& nextDiscountTTMTokenId6 <= 391);
\end{code}

@@

\begin{code}
0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.mutant.480.sol: 424contracts//0x534ccee849a688581d1b0c65e7ff317ed10c5ed3\_NametagToken.sol:650
        byte char = byte(bytes32(uint(x) * 2 ** (8 * j)));
 ==>  ...*...==>.../...
        byte char = byte(bytes32(uint(x) * 2 ** (8 / j)));
\end{code}
